---
title       : IS YOUR FOOD SAFE?
subtitle    : Outcome of Domestic Food Facilities Inspections
author      : Yi Liu
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap]  # mathjax, quiz, bootstrap
ext_widgets : {rCharts: libraries/nvd3} # {rCharts: ["libraries/highcharts",                                              # "libraries/nvd3", "libraries/morris"]}
mode        : selfcontained         # {standalone, draft}
knit        : slidify::knit2slides
---

# Introduction

## Some may think food safety is not a problem in US...  

### Over **300,000** Americans are hospitalized every year due to contaminated foods or beverages  
### **5,000** out of those end up with **_death_**  
  
  The Center for Food Safety and Applied Nutrition (CFSAN)
  is responsible for carrying out the inspections and specific tests        with only a little over 800 employees.
  
  This Shiny app will demostrate some results for the outcome of food
  safety inspection by CFSAN.

---
# Possible inspection outcomes: 
###    1. Official Action Indicated (**OAI**):  
        significant objectionable conditions are found and regulatory 
        action is warranted  
###    2. Voluntary Action Indicated (**VAI**):  
        objectionable conditions are found, but not at a level that 
        warrants regulatory action  
###    3. No Action Indicated (**NAI**):  
        no objectionable condition is found  

---
## Got interested?  

### example at next slide
[More at this Shiny App](https://chaorenliuyi.shinyapps.io/shiny)

### This is just a casual exploratory look for the food safety data
  
  
### Tons of places to look.  
  
[wiki page for __food safety risk analysis__](https://en.wikipedia.org/wiki/Food_safety_risk_analysis)  

[foodrisk.org](http://foodrisk.org/)  
# ...  
...

---
## Preliminary exploration 

```{r setup,cache = F, message = F, echo = F}
require(rCharts)
knitr::opts_chunk$set(comment = NA, results = 'asis', tidy = F, message = T)
```
```{r, echo = FALSE, results = 'hide', message=FALSE, warning=FALSE}
require(slidifyLibraries)
require(rCharts)
urban =readRDS('urban.rds')
```
```{r nvd3plot, results = 'asis', comment = NA, message = F, echo = F}
n1 <- nPlot(X ~ District.Decision, group = 'urban',
            type = 'multiBarChart', data = urban)
options(RCHART_WIDTH = 800, RCHART_HEIGHT = 550)
# n1$print("chart1", include_assets=TRUE, cdn=TRUE)
n1$show('inline', include_assets = TRUE, cdn = TRUE)
```




